---
title: "Wheeling Creek"
author: "Abigail O'Connor"
date: "3/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## loading data and packages

```{r wheeling data}
wheeling <- read.csv("Wheeling Creek Data.csv")
if(!require(ggplot2)){install.packages("ggplot2", dependencies = TRUE)}
library(ggplot2)
library(ggmap)
library(psych)          
library(nlme)
library(lme4)
library(vegan)
data <- subset(wheeling, E_coli_MPN != "NA")
model <- subset(wheeling, na.action = "na.omit")
new <- subset(data, Site != "Mouth")
up <- subset(data, Site == "Ranch Bar" | Site == "Cricket Hollow" | Site == "Grandstaff Run" | Site == "Britt's Run" | Site == "County Line Bridge" | Site == "Elm Grove Park")
down <- subset(data, Site == "Junior Ave" | Site == "Washington" | Site == "Kroger" | Site == "Fulton" | Site == "Tunnel Green")
names(wheeling)
head(data)
```
## checks
```{r checks}
shapiro.test(data$E_coli_MPN)
qqnorm(data$E_coli_MPN); qqline(data$E_coli_MPN)

data$log.coli <- log10(data$E_coli_MPN)
hist(data$log.coli)
shapiro.test(data$log.coli)
qqnorm(data$log.coli, ylim = c(0,5)); qqline(data$log.coli)

cor.test(data$E_coli_MPN, data$pH, method = "kendall")
cor.test(data$E_coli_MPN, data$pH, method = "spearman")
cor.test(data$E_coli_MPN, data$pH, method = "pearson")

wheeling.a <- (wheeling[,-(18:37)])
## removing NAs
wheeling.b <- wheeling.a[complete.cases(wheeling.a),]

library(usdm)

wc.VIF <- data.frame(scale(data$SPC),
                  scale(data$pH),
                  scale(data$DO),
                  scale(data$Turbidity),
                  scale(data$Temp),
                  scale(data$Cl),
                  scale(data$Prev_rain_cm),
                  scale(data$Rain_cm))
                  
wc.VIF.a <- vifstep(wc.VIF, th = 10)
wc.VIF.a

wcVIF <- data.frame(data$SPC, data$pH, data$DO, data$Turbidity, data$Temp, data$Cl, data$Prev_rain_cm, data$Rain_cm, data$Date, data$Flow_max, data$Developed_LMH)
                  
wcVIFa <- vifstep(wc.VIF, th = 10)
wcVIFa

```
## lmer
```{r models}
flmer <- lmer(E_coli_MPN ~  + (1 | Site), data = data)
flmer

##land use, km from mouth don't change by date
##flow doesn't change by site

confint(flmer)
random.effects(flmer)

lmer <- lmer(E_coli_MPN ~ scale(Turbidity) + scale(Temp) + scale(DO) + scale(SPC) + scale(H) + scale(Cl) + scale(Prev_rain_cm) + scale(Rain_cm) + scale(Flow_mean) + (1 | Site), data = data)
lmer

confint(lmer)
random.effects(lmer)

adonis(E_coli_MPN ~ Site, data = data)

dredge <- dredge(lmer)


e.c.wc <- lmer(E_coli_MPN ~ scale(SPC) + 
                 scale(pH) + 
                 scale(DO) +
                 scale(Turbidity) +
                 scale(Temp) +
                 scale(Cl) +
                 scale(Prev_rain_cm) +
                 scale(Rain_cm) +
                 (1 | Site), data = wheeling.b, REML = FALSE, na.action = "na.fail", control = lmerControl(optCtrl = list(maxfun=20000)))

e.c.wc.dredge <- dredge(e.c.wc)
e.c.wc.AIC <- model.avg(get.models(e.c.wc.dredge, subset = TRUE))
summary(e.c.wc.AIC)
confint(e.c.wc.AIC)
confint(lmer(E_coli_MPN~scale(Rain_cm) + (1|Site), data = data, REML = FALSE))

r.squaredGLMM(e.c.wc)
# this is the r2 of your whole model

r.squaredGLMM(lmer(E_coli_MPN ~ scale(Rain_cm) + (1|Site), data = data, REML=FALSE))
# the r2 of the top model
```
```


## entire creek graphs and data

```{r creek graphs}

#correlation scatter plots
#e. coli and turbidity
ggplot(data = new, aes(y = E_coli_MPN, x = Turbidity), stat = "identity", fill = "grey") + 
  geom_point() +
  geom_smooth(method = 'lm') +
  xlab("Turbidity") +
  ylab("MPN") + 
  scale_y_continuous(trans='log10') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#e. coli and rain
ggplot(data = new, aes(y = E_coli_MPN, x = Rain_cm), stat = "identity", fill = "grey") + 
  geom_point() +
  geom_smooth(method = 'lm') +
  xlab("Rain") +
  ylab("MPN") + 
  #scale_y_continuous(trans='log10') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#e. coli and SPC
ggplot(data = new, aes(y = E_coli_MPN, x = Cl), stat = "identity", fill = "grey") + 
  geom_point() +
  geom_smooth(method = 'lm') +
  xlab("SPC") +
  ylab("MPN") + 
  scale_y_continuous(trans='log10') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#e. coli and Km
ggplot(data = new, aes(y = Mean, x = Km), stat = "identity", fill = "grey") + 
  geom_point() +
  geom_smooth(method = 'lm') +
  xlab("check") +
  ylab("E. coli MPN (CFU)") + 
  scale_y_continuous(trans='log10') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

#r squared values
ggplotRegression <- function(fit){
  require(ggplot2)
  ggplot(fit$model, aes_string(x = names(fit$model)[1], y = names(fit$model)[2])) + 
    geom_point() +
    stat_smooth(method = "lm") +
    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       " P =",signif(summary(fit)$coef[2,4], 5))) +
    theme_classic() +
    xlab("check") +
    ylab("check")
}
ggplotRegression(lm(Turbidity ~ E_coli_MPN, data = new))

ggplotRegression(lm(Temp ~ E_coli_MPN, data = new))

ggplotRegression(lm(pH ~ E_coli_MPN, data = new))

ggplotRegression(lm(Flow_mean ~ E_coli_MPN, data = new))

ggplotRegression(lm(Developed_LMH ~ Mean, data = wheeling))

ggplotRegression(lm(Developed_LMH ~ Turb_mean, data = wheeling))
ggplotRegression(lm(Developed_LMH ~ Mean, data = wheeling))
ggplotRegression(lm(Developed_LMH ~ Temp_mean, data = wheeling))
ggplotRegression(lm(Developed_LMH ~ DO_mean, data = wheeling))
ggplotRegression(lm(Developed_LMH ~ pH_mean, data = wheeling))

ggplotRegression(lm(Km ~ Turb_mean, data = wheeling))
ggplotRegression(lm(Km ~ Mean, data = wheeling))
ggplotRegression(lm(Km ~ Temp_mean, data = wheeling))
ggplotRegression(lm(Km ~ DO_mean, data = wheeling))
ggplotRegression(lm(Km ~ pH_mean, data = wheeling))

print(wheeling$Km)

#reorder sites
data$Site <- factor(data$Site, levels = c("Ranch Bar","Cricket Hollow", "Grandstaff Run", "Britt's Run", "County Line Bridge", "Elm Grove Park", "Junior Ave", "Washington Ave", "Kroger", "Fulton", "Tunnel Green", "Mouth"))
print(levels(data$Site))

#bar graph with SE

groupmeans <- data.frame(E_coli_MPN = 0, SE = 0, Site = 0, Median = 0)
counter <- 1
for(i in levels(data$Site)){
  groupmeans[counter, 1] <- geometric.mean(subset(data, Site == as.character(i))$E_coli_MPN)
  groupmeans[counter, 2] <- sd(subset(data, Site == as.character(i))$E_coli_MPN)/
    sqrt(length(groupmeans[counter, 1] <- geometric.mean(subset(data, Site == as.character(i))$E_coli_MPN)))
  groupmeans[counter, 4] <- median(subset(data, Site == as.character(i))$E_coli_MPN)
  counter <- counter + 1 
}
groupmeans$Site <- as.vector (levels(data$Site))
print(groupmeans$Site)

groupmeans$Site <- factor(groupmeans$Site, levels = c("Ranch Bar","Cricket Hollow", "Grandstaff Run", "Britt's Run", "County Line Bridge", "Elm Grove Park", "Junior Ave", "Washington Ave", "Kroger", "Fulton", "Tunnel Green", "Mouth"))

ggplot() +
  geom_bar(data = data, aes(x = Site, y = E_coli_MPN), col = "black", fill = "grey", 
           stat = "summary", position = position_dodge()) + 
  geom_errorbar(data = groupmeans, aes(x = Site, ymin = E_coli_MPN - SE, ymax = E_coli_MPN + SE),
                width = 0.25, col = "black") +
  geom_hline(yintercept = 126, linetype = 1, col = "blue") +
  #geom_errorbar(data = groupmeans, aes(x = Site, ymin = Median, ymax = Median), 
                #col = "black", size = 1)+
  xlab("Site") +
  ylab("E. coli MPN (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  theme(axis.text.y = element_text(size = 10))

ggplot() +
  geom_bar(data = groupmeans, aes(x = Site, y = E_coli_MPN), col = "black", fill = "grey", 
           stat= "summary", position = position_dodge()) + 
  geom_errorbar(data = groupmeans, aes(x = Site, ymin = 0, ymax = E_coli_MPN + SE),
                width = 0.25, col = "black") +
  geom_hline(yintercept = 126, linetype = 1, col = "blue") +
  #geom_errorbar(data = groupmeans, aes(x = Site, ymin = Median, ymax = Median), col = "black", size = 1) +
  scale_y_continuous(breaks = c(0, 200, 400, 600, 800, 1000, 2000, 3000)) +
  xlab("Site") +
  ylab("E. coli MPN (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) +
  theme(axis.text.y = element_text(size = 12))
  ```

# box and whisker

data$Site <- factor(data$Site, levels = c("Ranch Bar","Cricket Hollow", "Grandstaff Run", "Britt's Run", "County Line Bridge", "Elm Grove Park", "Junior Ave", "Washington Ave", "Kroger", "Fulton", "Tunnel Green", "Mouth"))

ggplot(data = data, aes(x = Site, y = E_coli_MPN), col = "black", fill = "grey") +
  #scale_y_continuous(trans='log10') +
  geom_boxplot() +
  #geom_hline(yintercept = 126, linetype = 1, col = "blue") +
  xlab("Site") +
  ylab("E. coli MPN (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  theme(axis.text.y = element_text(size = 10))

ggplot(data = data, aes(x = Date, y = E_coli_MPN, color = Site, group = Site)) +
  geom_point() +
  #geom_hline(yintercept = 235, linetype = 1) +
  geom_line()+
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  scale_y_continuous(trans='log10') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Seasonal")

ggplot(data = data, aes(x = Date, y = E_coli_MPN)) +
  geom_boxplot() +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  scale_y_continuous(trans='log10') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Seasonal")

```

## site graphs and data

```{r site graphs}

#site codes
site1 <- subset(data, data$Site == "Ranch Bar")
site2 <- subset(data, data$Site == "Cricket Hollow")
site3 <- subset(data, data$Site == "Grandstaff Run")
site4 <- subset(data, data$Site == "Britt's Run")
site5 <- subset(data, data$Site == "County Line Bridge")
site6 <- subset(data, data$Site == "Elm Grove Park")
site7 <- subset(data, data$Site == "Junior Ave")
site8 <- subset(data, data$Site == "Washington Ave")
site9 <- subset(data, data$Site == "Kroger")
site10 <- subset(data, data$Site == "Fulton")
site11 <- subset(data, data$Site == "Tunnel Green")
site12 <- subset(data, data$Site == "Mouth")

mean(site1$E_coli_MPN)
max(site1$E_coli_MPN)
min(site1$E_coli_MPN)
median(site1$E_coli_MPN)
geometric.mean(site1$E_coli_MPN)
mean(data$E_coli_MPN)

#site correlations
ggplot(data = site8, aes(y = E_coli_MPN, x = Rain_cm), stat = "identity", fill = "grey") + 
  geom_point() +
  geom_smooth(method = 'lm') +
  xlab("Turbidity") +
  ylab("MPN") + 
  #scale_y_continuous(trans='log10') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggplotRegression <- function(fit){
  require(ggplot2)
  ggplot(fit$model, aes_string(x = names(fit$model)[1], y = names(fit$model)[2])) + 
    geom_point() +
    stat_smooth(method = "lm", col = "gold") +
    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       " P =",signif(summary(fit)$coef[2,4], 5))) +
    theme_classic() +
    xlab("Turbidity") +
    ylab("MPN E. coli (CFU)")
}
ggplotRegression(lm(Turbidity ~ E_coli_MPN, data = site1))


#barplot of site averages
ggplot(data = site1, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site1$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site1$Site)

ggplot(data = site2, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site2$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site2$Site)

ggplot(data = site3, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site3$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site3$Site)

ggplot(data = site4, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site4$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site4$Site)

ggplot(data = site5, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site5$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site5$Site)

ggplot(data = site6, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site6$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site6$Site)

ggplot(data = site7, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site7$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (NTU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site7$Site)

ggplot(data = site8, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site8$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site8$Site)

ggplot(data = site9, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site9$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site9$Site)

ggplot(data = site10, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site10$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site10$Site)

ggplot(data = site11, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site11$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site11$Site)

ggplot(data = site12, aes(x = Date, y = E_coli_MPN)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_hline(yintercept = mean(site12$E_coli_MPN), linetype = 2) +
  geom_hline(yintercept = 235, linetype = 1) +
  xlab("Collection Date") +
  ylab("MPN E. coli (CFU)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = site12$Site)

```

## site tables

```{r tables}
library(knitr)
library(kableExtra)
kable(wheeling[1:12, 14:19], col.names = c("Site","Coordinates", "Mean", "Median", "Min", "Max"), digits = 1) %>% 
kable_styling(bootstrap_options = c("striped", "hover"))

kable(wheeling[1:12, 14:15], col.names = c("Site","Coordinates")) %>%
kable_styling(bootstrap_options = c("striped", "hover"))

kable(wheeling[1:12, 21:26], col.names = c("Site", "Turbidity (NTU)","Temperature (°C)", "DO (mg/L)", "SPC (μS)", "pH")) %>%
kable_styling(bootstrap_options = c("striped", "hover"))

kable(wheeling[1:12, 28:29], col.names = c("Site", "Percent Exceedance")) %>%
kable_styling(bootstrap_options = c("striped", "hover"))
```

## map

```{r map}

register_google(key = "AIzaSyDliRRtVBUOQQQrNPl0gdY8vrp3LT77-hg")

map_all <- get_map(location = c(lon = -80.67, lat = 40.02), zoom = 12, maptype = c('hybrid'))  
## this sets the map area, bigger zoom number means more zoomed in

## x and y are the lat and long from the center point of the map 
## "data" is you data frame, "size" is your will be your ecoli data, you can divide the ecoli by a number to get the size right, it makes the dot smaller. My data frame is "N15_all", my values are "X15N". If you have issues, send me your data and I will see if I can get the code to work.
## "limites" are the range in data you want to include in the map

ggmap(map_all) +
  geom_point(aes(x = lon, y = lat, size = (30), colour = Mean), data = wheeling) + 
  scale_colour_continuous(name = 'E. coli (CFU/100mL)', limits = c(0,1000), low = "green", high = "red", space = "Lab", guide = "colorbar") + scale_size(guide='none', breaks = c(0, 1, 2, 3))
```
## land use data
```{r land use graphs}
landuse <- read.csv("landuse.csv")
lu <- read.csv("lu.csv")

landuse$Site <- factor(landuse$Site, levels = c("Ranch Bar","Cricket Hollow", "Grandstaff Run", "Britt's Run", "County Line", "Elm Grove", "Junior Ave", "Washington", "Kroger", "Fulton", "Tunnel Green", "Mouth"))

ggplot(data = landuse, aes (x = Site)) +
  geom_bar(aes(y = Developed_Total), stat = "identity", position = position_dodge()) +
  xlab("Site") +
  ylab("Percent Developed") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Land Use")

#geom_bar(aes(y = Pasture_Hay), 
  #         stat = "identity", position = position_dodge(), fill = "grey") +
 # scale_y_continuous(name = "Percent Developed", sec.axis = sec_axis(name="Percent Pasture")) + 

ggplot(data = landuse, aes (x = Site)) +
  geom_bar(aes(y = Pasture_Hay), stat = "identity", position = position_dodge()) +
  xlab("Site") +
  ylab("Percent Pasture") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Land Use")

lu$Site <- factor(lu$Site, levels = c("Ranch Bar","Cricket Hollow", "Grandstaff Run", "Britt's Run", "County Line", "Elm Grove", "Junior Ave", "Washington", "Kroger", "Fulton", "Tunnel Green", "Mouth"))

ggplot(data = lu, aes (x = Site)) +
  geom_bar(aes(y = Pasture_Hay), stat = "identity", position = position_dodge()) +
  xlab("Site") +
  ylab("Area Pasture (km2)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Land Use")

ggplot(data = lu, aes (x = Site)) +
  geom_bar(aes(y = Developed_Total), stat = "identity", position = position_dodge()) +
  xlab("Site") +
  ylab("Area Developed (km2)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Land Use")

ggplot(data = landuse, aes (x = Site)) +
  geom_bar(aes(y = Developed_LMH), stat = "identity", position = position_dodge()) +
  xlab("Site") +
  ylab("Area Developed (km2)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10)) +
  labs(title = "Land Use")

#correlations

ggplotRegression <- function(fit){
  require(ggplot2)
  ggplot(fit$model, aes_string(x = names(fit$model)[1], y = names(fit$model)[2])) + 
    geom_point() +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       " P =",signif(summary(fit)$coef[2,4], 5))) +
    theme_classic() +
    xlab("Percent Developed (Low, Med, High Intensity)") +
    ylab("Percent Exceedance")}

ggplotRegression(lm(E_coli ~ Developed_Total, data = landuse))
ggplotRegression(lm(Developed_LMH ~ Percent_Exceedance, data = landuse))
ggplotRegression(lm(Developed_Total ~ Percent_Exceedance, data = landuse))

ggplot(data = landuse, aes(y = Percent_Exceedance, x = Developed_Total), stat = "identity") + 
  geom_point(size = 3, col = "blue") +
  geom_smooth(method = 'lm', col = "blue") +
  xlab("Percent Developed") +
  ylab("Percent Exceedance") +
  #labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5)," P =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text.x = element_text(size = 12), axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12), axis.title.y = element_text(size = 12), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

```


